---
title: "EU_A_new"
format: html
editor: visual
---

## Group assignment

The aim of this group assignment is to tidy both files so that they adhere to all four data tidying principles.

1.  Each type of case must have its own tibble

2.  Each observation must have its own row

3.  Each variable must have its own column

4.  Each value must have its own cell.

Mai's RQ:

*RQ1: To what extent is people's attitude toward the EU and their political cynicism developed throughout the EU election?*

*RQ2: To what extent is people's attitude toward the EU and their political cynicism related to the media content they were exposed to?*

In the All_Waves document, variables needed:

`Political cynicism`: Q10 (wave 1), Q07 (wave 2), Q11 (wave 3), Q13 (wave 4)\
`EU-attitudes`: Q26, Q27 (wave 1), Q22, Q23 (wave 2), Q28, Q29 (wave 3), Q31, Q32 (wave4)Notes: In wave 1, 7 = pro EU for all nine items of Q26. In Q27, 7 = pro-EU for item 1, 2, 3, 4, 9 ;while 7 = against EU for item 5, 6, 7, 8.

`self reported media exposure (TV)`: Q49 (wave 1), Q44 (wave 2) Q43 (wave 3) Q47 (wave 4)

*`self reported media exposure (newspapers)`: Q50 (wave 1) Q45 (wave 2) Q44 (wave 3) Q48 (wave 4)*

`self reported media exposure (Internet)`: Q51 (wave 1) Q46 (wave 2) Q45 (wave 3) Q49 (wave 4)

In the content analysis documents, variables needed:

`V11`: How does the specific media evaluate the EU

`V12`: How does the specific media evaluate the European Parliament

`V13`: If the specific media mention a certain aspect related to the state of democracy in the EU and how do they evaluate it.

Bará's RQs:

Sará's RQs:

## 1. Rename variables

In the raw file, most of the variable names are structured in such a way that it has different question number in different waves.

For instance: `Political cynicism`: Q10 (wave 1), Q07 (wave 2), Q11 (wave 3), Q13 (wave 4).

Therefore, it is easier for further tidying if we capture all four questions measuring a certain variable in different waves and rename them into a consistent name e.g., `w1_polcyn_1`, `w2_polcyn_2`, etc.

This data tidying process main tackles principle 1: Each type of case must have its own tibble

## 2. Split tibble (Principle 1)

```{r}
# we first split the ALL_WAVES df into two tibbles: "demographic" & "waves"



# We then split the content analysis df into two tibbles: the variables that we need and the one that will not be cleaned


# Finally, we split the "waves" df into two tibbles, the one contains variabels that we need and the other that contains variables that will not be used


```

## 3. Pivot_longer all the items information (Principle 2)

In the new tibble "waves", we see many variables that are measured with several items. This violates the data tidying principle 2, namely *each observation must have its own row*. To address this, we use function `pivot_longer()`. **(items)**

```{r}
# pivot_longer() tackling items. The code should create a new column: item_variablename


```

Now further applying the second principle, we should also deal with the waves information within the column's name. (**waves**)

```{r}
# pivot_longer() tackling waves information. This code should create a new column: wave capturing in which wave is this certain input collected

```

## 4. Separate numbers with labels (Principle 4)

Principle 4 of the tidy tidying principle is: Each value must have its own cell.

We should get rid of the textual explanation within each input (e.g., 1 helemaal mee oneens) by creating a new column capturing the label information.

```{r}
# this code should create a new column to capture the label information

```

## 4. In the content analysis we use separate_wider (Principle 3)
