---
title: "EU_A_new"
format: html
editor: visual
---

## Group assignment

The aim of this group assignment is to tidy both files so that they adhere to all four data tidying principles.

1.  Each type of case must have its own tibble

2.  Each observation must have its own row

3.  Each variable must have its own column

4.  Each value must have its own cell.

Mai's RQ:

*RQ1: To what extent is people's attitude toward the EU and their political cynicism developed throughout the EU election?*

*RQ2: To what extent is people's attitude toward the EU and their political cynicism related to the media content they were exposed to?*

In the All_Waves document, variables needed:

| ***Panel Survey*** |   |   |   |   |
|---------------|---------------|---------------|---------------|---------------|
| **Variable** | **Wave 1** | **Wave 2** | **Wave 3** | **Wave 4** |
| Political cynicism | Q10 | Q7 | Q11 | Q13 |
| EU attitudes | Q26, Q27 | Q22, Q23 | Q28, Q29 | Q31, Q32 |
| Self reported media exposure (TV) | Q49 | Q44 | Q43 | Q47 |
| Self reported media exposure (newspapers) | Q50 | Q45 | Q44 | Q48 |
| Self reported media exposure (Internet) | Q51 | Q46 | Q45 | Q49 |

Notes: In wave 1, 7 = pro EU for all nine items of Q26. In Q27, 7 = pro-EU for item 1, 2, 3, 4, 9 ;while 7 = against EU for item 5, 6, 7, 8.

| *Content analysis* |   |
|----|----|
| **Variable** | **Label** |
| How does the specific media evaluate the EU | V11 |
| How does the specific media evaluate the European Parliament | V12 |
| If the specific media mention a certain aspect related to the state of democracy in the EU and how do they evaluate it. | V13 |

In the content analysis documents, variables needed:

`V11`: How does the specific media evaluate the EU

`V12`: How does the specific media evaluate the European Parliament

`V13`: If the specific media mention a certain aspect related to the state of democracy in the EU and how do they evaluate it.

Bará's RQs:

1.  How does the readership of Dutch media outlets differ in their attitudes regarding migration?

2.  How do Dutch media outlets cover migration?

Variables Barbora:

| ***Panel Survey***          |            |            |            |            |
|-----------------|--------------|--------------|--------------|--------------|
| **Variable**                | **Wave 1** | **Wave 2** | **Wave 3** | **Wave 4** |
| Most important issue        | Q01        | Q01        | Q01        | Q01        |
| Intergroup comfort: Muslims | Q54        | Q48        |            |            |
| Intergroup comfort: Poles   | Q56        | Q49        |            |            |
| Ethnic minority             | Q68        |            |            |            |
| Anti-immigrant attitudes    | Q42        | Q39        |            |            |
| Immigrant follow up         | Q43        | Q40        |            |            |

| *Content analysis* |            |
|--------------------|------------|
| **Variable**       | **Label**  |
| Outlet             | V4         |
| Topic              | V6_cleaned |
| Day                | V3a        |
| Month              | V3b        |
| Year               | V3c        |
| Emotion            | NL1 a-f    |
| Mention Muslims    | NL2        |
| Evaluation Muslims | NL3        |
| Mention Poles      | NL4        |
| Evaluation Poles   | NL5        |

Sará's RQs:

How does the intention to vote differ between EU and local elections, and what is the relationship between the difference and national identity, attitude towards globalisation and anti-immigrant attitudes 6 months prior to the EU elections in regards to the media outlet voters are consuming content from?

Sará's RQs:

| ***Panel survey***             |        |        |        |        |
|--------------------------------|--------|--------|--------|--------|
| **Variable**                   | Wave 1 | Wave 2 | Wave 3 | Wave 4 |
| National identity              | Q05    |        |        |        |
| Attitudes globalisation        | Q32    |        |        |        |
| Vote intention EU              | Q34    | Q35    | Q07    |        |
| Vote intention local elections | Q39    |        |        |        |
| Anti-immigrant attitudes       | Q42    | Q39    |        |        |
| Highest completed education    | Q61    |        |        |        |
| Income                         | Q65    |        |        |        |
| Employment status              | Q67    |        |        |        |
| Age                            |        |        |        |        |
| Gender                         |        |        |        |        |

| *Content analysis* |           |
|--------------------|-----------|
| **Variable**       | **Label** |
| Outlet             | V4        |

## 1. Rename variables

In the raw file, most of the variable names are structured in such a way that it has different question number in different waves.

For instance: `Political cynicism`: Q10 (wave 1), Q07 (wave 2), Q11 (wave 3), Q13 (wave 4).

Therefore, it is easier for further tidying if we capture all four questions measuring a certain variable in different waves and rename them into a consistent name e.g., `w1_polcyn_1`, `w2_polcyn_2`, etc.

This data tidying process adheres data tidying principle 1: Each type of case must have its own tibble.

First, we import relevant R library and dataset.

```{r}
library(tidyverse)
```

```{r}
# Import two data sets. Change the path name to the relative ones if needed
EU_2014 <- read.csv('/Users/mycroftzhang/Downloads/Using R/EU2014/All waves GENERAL.csv')
content_analysis <- read.csv('/Users/mycroftzhang/Downloads/Using R/EU2014/Dataset MCA EPE 2014 NL FINAL.csv')
```

Now rename variables:

```{r}
# giving columns informative names, translating dutch names
EU_2014_renamed <- EU_2014 |>
rename(
  intnr = INTNR,
  respnr = RESPNR,
  sample = SAMPLE,
  waves = WAVES,
  weight_w1 = GEWICHTA1_w1,
  weight_w2 = GEWICHTA1_w2,
  weight_w3 = GEWICHTA1_w3,
  weight_w4 = GEWICHTA1_w4,
  gender = GSL,
  age = LFT,
  education = OPLA,
  region = NIELSENCBS, 
  family_size = GEZINSGROOTTE,
  pol2012 = POL2012,
  w1_date = w1_DATUM,
  w1_time = w1_TIJD,
  w2_date = w2_DATUM,
  w2_time = w2_TIJD,
  w3_date = w3_DATUM,
  w3_time = w3_TIJD,
  w4_date = w4_DATUM,
  w4_time = w4_TIJD,
) 
colnames(EU_2014_renamed) <- tolower(colnames(EU_2014_renamed)) 
colnames(content_analysis) <- tolower(colnames(content_analysis))
# this function changes all column names to lowercase 
# (more consistent and easy to use)
```

## 2. Select the variables that will be used in the analysis (Principle 1)

Before splitting the tibble "EU_2014_renamed", we believe that `intnr` and `respnr` could both independently uniquely identify each input, thus both could act as the primary key. Out of convenience, we use `respnr` as the primary key.

```{r}
EU_2014_renamed |> 
  count(intnr) |> 
  filter(n >1)

EU_2014_renamed |> 
  count(respnr) |> 
  filter(n>1)
```

We are extracting and creating a new tibble out of the tibble "EU_2014_renamed" (the table containing all survey data), namely "EU_needed".

We also extract variables that will be further processed in our analysis out of the "content_analysis" tibble, namely "ca_needed"

```{r}
# We then split the content analysis df into two tibbles: the variables that we need and the one that will not be cleaned

ca_needed <- content_analysis |> 
  select(
        v11, v12, v13, # Mai's variables
        v4, v3a, v3b, v3c, v6_cleaned, #Barbora's variables
        nl1a:nl1f, 
        nl2_1_1:nl2_4_3, 
        nl3, 
        nl4_1_1:nl4_4_3, 
        nl5,
        v4 # Sara's variable
  )

# Now, we split the "all_waves" df into two tibbles, one contains variables that we need for further analysis and the other that contains variables that will not be used

EU_2014_cleaned <- all_waves |> 
  select(
        intnr, respnr, sample, waves,
        w1_date, w1_time, w2_date, w2_time, w3_date,
        w3_time, w4_date, w4_time, 
        w1_q1, w2_q1, w3_q1, w4_q1, # Barbora's variables
        starts_with("w1_q54"), starts_with("w1_q56"),
        starts_with("w1_q68"), starts_with("w1_q42"),
        starts_with("w1_q43"), starts_with("w2_q48"),
        starts_with("w2_q49"), starts_with("w2_q39"),
        starts_with("w2_q40"), 
        starts_with("w1_q10"), starts_with("w2_q7"), # Mai's variables
        starts_with("w3_q11"), starts_with("w4_q13"),
        starts_with("w1_q26"), starts_with("w1_q27"),
        starts_with("w2_q22"), starts_with("w2_q23"),
        starts_with("w3_q28"), starts_with("w3_q29"),
        starts_with("w4_q31"), starts_with("w4_q32"),
        starts_with("w1_q49"), starts_with("w2_q44"),
        starts_with("w3_q43"), starts_with("w4_q47"),
        starts_with("w1_q50"), starts_with("w2_q45"),
        starts_with("w3_q44"), starts_with("w1_q51"),
        starts_with("w2_q46"), starts_with("w3_q45"),
        starts_with("w4_q49"),
        starts_with("w1_q5"), starts_with("w1_q32"), # Sara's variables
        starts_with("w1_q34"), starts_with("w2_q35"),
        starts_with("w3_q7"), starts_with("w1_q39"),
        starts_with("w1_q42"), starts_with("w2_q39"),
        starts_with("w1_q61"), starts_with("w1_q65"),
        starts_with("w1_q67")
  )
```

After splitting, we have two working tibbles:

1\) `EU_2014_cleaned` this contains all the variables that will be included in further analysis

3\) `ca_needed` this tibble contains all the variables that will be included in the further analysis that is related to the content analysis.

## 3. Giving variables more informative names

Since the variable names in the document is in the format of "w1_q1_1" where the question number differs across different wave. We would like to standardise variable names.

```{r}
# creating a vector capturing column names
EU_2014_cleaned <- EU_2014_cleaned |> 
    rename_with(function(x) gsub("w1_q5", "w1_national_identity", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q32", "w1_attitude_global", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q34", "w1_vote_intention_eu", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q39", "w1_vote_intention_local", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q42", "w1_anti_immigrant", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q10", "w1_political_cynicism", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q7", "w2_political_cynicism", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w3_q11", "w3_political_cynicism", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w4_q13", "w4_political_cynicism", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q26", "w1_eu_attitude", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q22", "w2_eu_attitude", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w3_q28", "w3_eu_attitude", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w4_q31", "w4_eu_attitude", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q27", "w1_eu_attitude2", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w3_q29", "w3_eu_attitude2", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w3_q29", "w3_eu_attitude2", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w4_q32", "w4_eu_attitude2", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q49", "w1_media_exposure_tv", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q44", "w2_media_exposure_tv", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w3_q43", "w3_media_exposure_tv", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w4_q47", "w4_media_exposure_tv", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q50", "w1_media_exposure_newspaper", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q45", "w2_media_exposure_newspaper", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w3_q44", "w3_media_exposure_newspaper", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w4_q48", "w4_media_exposure_newspaper", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q51", "w1_media_exposure_internet", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q46", "w2_media_exposure_internet", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w3_q45", "w3_media_exposure_internet", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w4_q49", "w4_media_exposure_internet", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q1", "w1_most_important_issue", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q1", "w2_most_important_issue", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w3_q1", "w3_most_important_issue", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w4_q1", "w4_most_important_issue", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q54", "w1_comfort_muslims", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q48", "w2_comfort_muslims", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q56", "w1_comfort_poles", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q49", "w2_comfort_poles", x, fixed = TRUE)) |>
    rename(
      w1_ethnic_minority = w1_q68) |>
    rename(
      w1_ethnic_minority_specification = w1_q68_yes) |>
    rename_with(function(x) gsub("q39", "anti_immigrant_attitudes", x, fixed = TRUE)) |>
    rename(
      w1_immigrant_followup = w1_q43) |>
    rename(
      w2_immigrant_followup = w2_q40)
    rename(
      w1_highest_completed_education = w1_q61) |>
    rename(
      w1_income = w1_q65) |>    
    rename(
      w1_employment_status = w1_q67)

```

## 4. Separate numbers with labels (Principle 4)

Principle 4 of the tidy tidying principle is: Each value must have its own cell.

We should get rid of the textual explanation within each input (e.g., 1 helemaal mee oneens) by creating a new column capturing the label information.

```{r}

# creating a vector capturing column names that have cells which include a number and its label
# this vector will be used to select these columns from the dataset within separate_wider

columns_for_separation <- EU_2014_cleaned |>
  select_if(function(col) any(grep("1 hele|1 geen", col))) |> # selects only columns with cells
  colnames()   # keeps only the names of the columns          # incl pattern in grep()

```

```{r}
# separating scores and labels into two separate columns

EU_2014_cleaned <- EU_2014_cleaned |>
  separate_wider_delim(
    cols = all_of(columns_for_separation), # takes columns the names of which are in the object
    delim = stringr::regex(" (?=helemaal*)|(?=heel*)|(?=in redelijke mate)|(?=een beetje)|(?=zeer goed)|(?=geen)|(?=ongeveer)|(?=bijna alleen maar)"), # specifies the delim pattern
    names_sep = "_",     # new columns given the old name "_" and a number
    too_few = "align_start", 
    cols_remove = TRUE
) 
```

## 5. Pivot_longer all the items information (Principle 2)

In the new tibble "waves", we see many variables that are measured with several items. This violates the data tidying principle 2, namely *each observation must have its own row*. To address this, we use function `pivot_longer()`. **(items)**

```{r}
# pivot_longer() tackling items. The code should create a new column: item_variablename


```

Now further applying the second principle, we should also deal with the waves information within the column's name. (**waves**)

```{r}
# pivot_longer() tackles waves information. This code should create a new column: wave capturing in which wave is this certain input collected

```

## 6. Determine the primary keys and foreign keys of the table

After applying the first the second principle of data tidying, now we come to decide upon the primary keys and foreign keys in each tibbles.
We will separate the tibble "EU_2014_cleaned" into two tibbles: "demographic" and "waves"

First, `respnr` act as the primary key for tibble \`demographic\`

```{r}
demographic |> 
  count(respnr) |> 
  filter(n>1)
```

`respnr` and `waves` together act as the primary key for tibble ""

```{r}

```

## 7. In the content analysis we use separate_wider (Principle 3)
