---
title: "Group project merged"
format: html
editor: visual
---

## Group: EU (A)

## 

```{r}
# Importing tideverse
library(tidyverse)
```

## Importing the dataset

```{r}
# Load data set
EU_2014_cleaned <- read_csv('EU2014/All waves GENERAL.csv')
```

## RQs overview BÁRA AND SÁRA NEED TO ADD RQ

1.  To what extent is people's attitude toward the EU, people's economic evaluation toward the EU, and their political cynicism developed throughout the EU election?

2.  To what extent is people's attitude toward the EU, people's economic evaluation toward the EU and their political cynicism related to their media use pattern?

3.  How does the intention to vote differ between EU and local elections, and what is the relationship between the difference and national identity, attitude towards globalisation and anti-immigrant attitudes 6 months prior to the EU elections?

    \

## Variables needed - ASK TOMORROW IF WE SHOULD KEEP ONLY WHAT WE ARE USING

## Renaming demographics

```{r}
# giving columns informative names, translating dutch names and lowercasing all letters: DEMOGRAPHICS AND DATA SET INFO
EU_2014_cleaned <- EU_2014_cleaned |>
rename(
  weight_w1 = GEWICHTA1_w1,
  weight_w2 = GEWICHTA1_w2,
  weight_w3 = GEWICHTA1_w3,
  weight_w4 = GEWICHTA1_w4,
  gender = GSL,
  age = LFT,
  education = OPLA,
  region = NIELSENCBS, 
  family_size = GEZINSGROOTTE,
  w1_date = w1_DATUM,
  w1_time = w1_TIJD,
  w2_date = w2_DATUM,
  w2_time = w2_TIJD,
  w3_date = w3_DATUM,
  w3_time = w3_TIJD,
  w4_date = w4_DATUM,
  w4_time = w4_TIJD,
) 

colnames(EU_2014_cleaned) <- tolower(colnames(EU_2014_cleaned))
```

## Parsing values in cells - LETS ASK TOMORROW (based on that Bára's part either stays or needs to be rewritten)

```{r}
# Value will be parsed in only numerical forms
EU_2014_cleaned <- EU_2014_cleaned |> 
  mutate(
    across(c(
              w1_q32_1, w1_q32_1
            ), parse_number)
          )

# We start with parsing variable: Political cynicism
EU_2014_cleaned <- EU_2014_cleaned |> 
  mutate(
    across(c(
              w1_q10_1, w1_q10_2, w1_q10_3, w1_q10_4,
              w2_q7_1, w2_q7_2, w2_q7_3, w2_q7_4,
              w3_q11_1, w3_q11_2, w3_q11_3, w3_q11_4,
              w4_q13_1, w4_q13_2, w4_q13_3, w4_q13_4
            ), parse_number)
          )

# Now parse variable: EU-attitude
EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(across(c(w1_q26_1:w1_q26_9, w1_q27_1:w1_q27_9,
                  w2_q22_1:w2_q22_9, w2_q23_1:w2_q23_9,
                  w3_q28_1:w3_q28_9, w3_q29_1:w3_q29_9,
                  w4_q31_1:w4_q31_9, w4_q32_1:w4_q32_9),
                parse_number)
               )

# For variable: Economic evaluation
EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(across(c(w1_q12, w2_q9, w3_q13, w4_q15),
                parse_number)
               )

# For variable: self reported media exposure (TV)
EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(across(c(w1_q49_1 : w1_q49_10,
                  w2_q44_1 : w2_q44_10,
                  w3_q43_1 : w3_q43_10,
                  w4_q47_1 : w4_q47_10
                  ),
                parse_number)
                )
 # For variable: self reported media exposure (newspaper)
EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(across(c(w1_q50_1 : w1_q50_10,
                  w2_q45_1 : w2_q45_10,
                  w3_q44_1 : w3_q44_10,
                  w4_q48_1 : w4_q48_10
                  ),
                parse_number)
                )
# Finally, for variable: self reported media exposure (Internet)
EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(across(c(w1_q51_1, w1_q51_2, w1_q51_5, w1_q51_6,
                  w2_q46_1, w2_q46_2, w2_q46_5, w2_q46_6,
                  w3_q45_1, w3_q45_2, w3_q45_5, w3_q45_6,
                  w4_q49_1, w4_q49_2, w4_q49_5, w4_q49_6
                  ),
                parse_number)
                )
EU_2014_cleaned <- EU_2014_cleaned |>
  rename(
    w1_most_important_issue = w1_q1,
    w2_most_important_issue = w2_q1,
    w3_most_important_issue = w3_q1,
    w4_most_important_issue = w4_q1)

EU_2014_cleaned <- EU_2014_cleaned |>
    rename_with(function(x) gsub("w1_q54","w1_comfort_muslims", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q56", "w1_comfort_poles", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q48","w2_comfort_muslims", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q49", "w2_comfort_poles", x, fixed = TRUE)) |>
    rename(
      w1_ethnic_minority = w1_q68) |>
    rename(
      w1_ethnic_minority_specification = w1_q68_yes) |>
    rename_with(function(x) gsub("q39", "anti_immigrant_attitudes", x, fixed = TRUE)) |>
    rename(
      w1_immigrant_followup = w1_q43) |>
    rename(
      w2_immigrant_followup = w2_q40) |>
    rename(
      w2_media_trust_rtl = w2_q27_1,
      w2_media_trust_nos = w2_q27_2,
      w2_media_trust_telegraaf = w2_q28_1,
      w2_media_trust_nrc = w2_q28_2,
      w2_media_trust_volkskrant = w2_q28_6,
      w2_media_trust_nunl = w2_q28_11
    )

```

## Adjusting time and date variables

```{r}
# using lubridate to set dates in date format

EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(
    across(c(w1_date, w2_date, w3_date, w4_date), ymd)
  )

```

## Renaming variable names 

```{r}
EU_2014_cleaned <- EU_2014_cleaned |> 
# we need to give all variables informative name so the variables can be pivoted later.
EU_2014_cleaned |> 
  rename(
    w1_nationalidentity_1 = w1_q5_1,
    w1_nationalidentity_2 = w1_q5_2,
    w1_nationalidentity_3 = w1_q5_3,
    w1_nationalidentity_4 = w1_q5_4,
    w1_attitudeglobal_1 = w1_32_1,
    w1_attitudeglobal_2 = w1_32_2,
    w1_attitudeglobal_3 = w1_32_3,
    w1_attitudeglobal_4 = w1_32_4,
    w1_voteintenteu = w1_q34,
    w1_voteintenteu_other = w1_q34_OTHER,
    w1_voteintentlocal = w1_q39,
    w1_voteintentlocal_other = w1_q39_OTHER,
    w1_antiimmigrant_1 = w1_q42_1,
    w1_antiimmigrant_2 = w1_q42_2,
    w1_antiimmigrant_3 = w1_q42_3,
    w1_antiimmigrant_4 = w1_q42_4,
    w1_antiimmigrant_5 = w1_q42_5,
  )

pol_cyn = c(w1_polcyn_1 = "w1_q10_1",
              w1_polcyn_2 = "w1_q10_2",
              w1_polcyn_3 = "w1_q10_3",
              w1_polcyn_4 = "w1_q10_4",
              w2_polcyn_1 = "w2_q7_1",
              w2_polcyn_2 = "w2_q7_2",
              w2_polcyn_3 = "w2_q7_3",
              w2_polcyn_4 = "w2_q7_4",
              w3_polcyn_1 = "w3_q11_1",
              w3_polcyn_2 = "w3_q11_2",
              w3_polcyn_3 = "w3_q11_3",
              w3_polcyn_4 = "w3_q11_4",
              w4_polcyn_1 = "w4_q13_1",
              w4_polcyn_2 = "w4_q13_2",
              w4_polcyn_3 = "w4_q13_3",
              w4_polcyn_4 = "w4_q13_4"
              )
  eu_att1 = c(w1_eu_att1_1 = "w1_q26_1",
              w1_eu_att1_2 = "w1_q26_2",
              w1_eu_att1_3 = "w1_q26_3",
              w1_eu_att1_4 = "w1_q26_4",
              w1_eu_att1_5 = "w1_q26_5",
              w1_eu_att1_6 = "w1_q26_6",
              w1_eu_att1_7 = "w1_q26_7",
              w1_eu_att1_8 = "w1_q26_8",
              w1_eu_att1_9 = "w1_q26_9",
              w2_eu_att1_1 = "w2_q22_1",
              w2_eu_att1_2 = "w2_q22_2",
              w2_eu_att1_3 = "w2_q22_3",
              w2_eu_att1_4 = "w2_q22_4",
              w2_eu_att1_5 = "w2_q22_5",
              w2_eu_att1_6 = "w2_q22_6",
              w2_eu_att1_7 = "w2_q22_7",
              w2_eu_att1_8 = "w2_q22_8",
              w2_eu_att1_9 = "w2_q22_9",
              w3_eu_att1_1 = "w3_q28_1",
              w3_eu_att1_2 = "w3_q28_2",
              w3_eu_att1_3 = "w3_q28_3",
              w3_eu_att1_4 = "w3_q28_4",
              w3_eu_att1_5 = "w3_q28_5",
              w3_eu_att1_6 = "w3_q28_6",
              w3_eu_att1_7 = "w3_q28_7",
              w3_eu_att1_8 = "w3_q28_8",
              w3_eu_att1_9 = "w3_q28_9",
              w4_eu_att1_1 = "w4_q31_1",
              w4_eu_att1_2 = "w4_q31_2",
              w4_eu_att1_3 = "w4_q31_3",
              w4_eu_att1_4 = "w4_q31_4",
              w4_eu_att1_5 = "w4_q31_5",
              w4_eu_att1_6 = "w4_q31_6",
              w4_eu_att1_7 = "w4_q31_7",
              w4_eu_att1_8 = "w4_q31_8",
              w4_eu_att1_9 = "w4_q31_9"
              )
  eu_att2 = c(w1_eu_att2_1 = "w1_q27_1",
              w1_eu_att2_2 = "w1_q27_2",
              w1_eu_att2_3 = "w1_q27_3",
              w1_eu_att2_4 = "w1_q27_4",
              w1_eu_att2_5 = "w1_q27_5",
              w1_eu_att2_6 = "w1_q27_6",
              w1_eu_att2_7 = "w1_q27_7",
              w1_eu_att2_8 = "w1_q27_8",
              w1_eu_att2_9 = "w1_q27_9",
              w1_eu_att2_1 = "w1_q27_1",
              w1_eu_att2_2 = "w1_q27_2",
              w1_eu_att2_3 = "w1_q27_3",
              w1_eu_att2_4 = "w1_q27_4",
              w1_eu_att2_5 = "w1_q27_5",
              w1_eu_att2_6 = "w1_q27_6",
              w1_eu_att2_7 = "w1_q27_7",
              w1_eu_att2_8 = "w1_q27_8",
              w1_eu_att2_9 = "w1_q27_9",
              w3_eu_att2_1 = "w3_q29_1",
              w3_eu_att2_2 = "w3_q29_2",
              w3_eu_att2_3 = "w3_q29_3",
              w3_eu_att2_4 = "w3_q29_4",
              w3_eu_att2_5 = "w3_q29_5",
              w3_eu_att2_6 = "w3_q29_6",
              w3_eu_att2_7 = "w3_q29_7",
              w3_eu_att2_8 = "w3_q29_8",
              w3_eu_att2_9 = "w3_q29_9",
              w4_eu_att2_1 = "w4_q32_1",
              w4_eu_att2_2 = "w4_q32_2",
              w4_eu_att2_3 = "w4_q32_3",
              w4_eu_att2_4 = "w4_q32_4",
              w4_eu_att2_5 = "w4_q32_5",
              w4_eu_att2_6 = "w4_q32_6",
              w4_eu_att2_7 = "w4_q32_7",
              w4_eu_att2_8 = "w4_q32_8",
              w4_eu_att2_9 = "w4_q32_9"
             )
  econ_eval = c(w1_econ_eval = "w1_q12",
                w2_econ_eval = "w2_q9",
                w3_econ_eval = "w3_q13",
                w4_econ_eval = "w4_q15"
              )
  media_tv = c( w1_media_tv_1  = "w1_q49_1",
                w1_media_tv_2  = "w1_q49_2",
                w1_media_tv_3  = "w1_q49_3",
                w1_media_tv_4  = "w1_q49_4",
                w1_media_tv_5  = "w1_q49_5",
                w1_media_tv_6  = "w1_q49_6",
                w1_media_tv_7  = "w1_q49_7",
                w1_media_tv_8  = "w1_q49_8",
                w1_media_tv_9  = "w1_q49_9",
                w1_media_tv_10 = "w1_q49_10",
                w2_media_tv_1  = "w2_q44_1",
                w2_media_tv_2  = "w2_q44_2",
                w2_media_tv_3  = "w2_q44_3",
                w2_media_tv_4  = "w2_q44_4",
                w2_media_tv_5  = "w2_q44_5",
                w2_media_tv_6  = "w2_q44_6",
                w2_media_tv_7  = "w2_q44_7",
                w2_media_tv_8  = "w2_q44_8",
                w2_media_tv_9  = "w2_q44_9",
                w2_media_tv_10 = "w2_q44_10",
                w3_media_tv_1  = "w3_q43_1",
                w3_media_tv_2  = "w3_q43_2",
                w3_media_tv_3  = "w3_q43_3",
                w3_media_tv_4  = "w3_q43_4",
                w3_media_tv_5  = "w3_q43_5",
                w3_media_tv_6  = "w3_q43_6",
                w3_media_tv_7  = "w3_q43_7",
                w3_media_tv_8  = "w3_q43_8",
                w3_media_tv_9  = "w3_q43_9",
                w3_media_tv_10 = "w3_q43_10",
                w4_media_tv_1  = "w4_q47_1",
                w4_media_tv_2  = "w4_q47_2",
                w4_media_tv_3  = "w4_q47_3",
                w4_media_tv_4  = "w4_q47_4",
                w4_media_tv_5  = "w4_q47_5",
                w4_media_tv_6  = "w4_q47_6",
                w4_media_tv_7  = "w4_q47_7",
                w4_media_tv_8  = "w4_q47_8",
                w4_media_tv_9  = "w4_q47_9",
                w4_media_tv_10 = "w4_q47_10"
              )
  media_paper = c(w1_media_np_1  = "w1_q50_1",
                  w1_media_np_2  = "w1_q50_2",
                  w1_media_np_3  = "w1_q50_3",
                  w1_media_np_4  = "w1_q50_4",
                  w1_media_np_5  = "w1_q50_5",
                  w1_media_np_6  = "w1_q50_6",
                  w1_media_np_7  = "w1_q50_7",
                  w1_media_np_8  = "w1_q50_8",
                  w1_media_np_9  = "w1_q50_9",
                  w1_media_np_10 = "w1_q50_10",
                  w2_media_np_1  = "w2_q45_1",
                  w2_media_np_2  = "w2_q45_2",
                  w2_media_np_3  = "w2_q45_3",
                  w2_media_np_4  = "w2_q45_4",
                  w2_media_np_5  = "w2_q45_5",
                  w2_media_np_6  = "w2_q45_6",
                  w2_media_np_7  = "w2_q45_7",
                  w2_media_np_8  = "w2_q45_8",
                  w2_media_np_9  = "w2_q45_9",
                  w2_media_np_10 = "w2_q45_10",
                  w3_media_np_1  = "w3_q44_1",
                  w3_media_np_2  = "w3_q44_2",
                  w3_media_np_3  = "w3_q44_3",
                  w3_media_np_4  = "w3_q44_4",
                  w3_media_np_5  = "w3_q44_5",
                  w3_media_np_6  = "w3_q44_6",
                  w3_media_np_7  = "w3_q44_7",
                  w3_media_np_8  = "w3_q44_8",
                  w3_media_np_9  = "w3_q44_9",
                  w3_media_np_10 = "w3_q44_10",
                  w4_media_np_1  = "w4_q48_1",
                  w4_media_np_2  = "w4_q48_2",
                  w4_media_np_3  = "w4_q48_3",
                  w4_media_np_4  = "w4_q48_4",
                  w4_media_np_5  = "w4_q48_5",
                  w4_media_np_6  = "w4_q48_6",
                  w4_media_np_7  = "w4_q48_7",
                  w4_media_np_8  = "w4_q48_8",
                  w4_media_np_9  = "w4_q48_9",
                  w4_media_np_10 = "w4_q48_10"
                 )
  media_int = c(w1_media_int_1 = "w1_q51_1",
                w1_media_int_2 = "w1_q51_2",
                w1_media_int_3 = "w1_q51_5",
                w1_media_int_4 = "w1_q51_6",
                w2_media_int_1 = "w2_q46_1",
                w2_media_int_2 = "w2_q46_2",
                w2_media_int_3 = "w2_q46_5",
                w2_media_int_4 = "w2_q46_6",
                w3_media_int_1 = "w3_q45_1",
                w3_media_int_2 = "w3_q45_2",
                w3_media_int_3 = "w3_q45_5",
                w3_media_int_4 = "w3_q45_6",
                w4_media_int_1 = "w4_q49_1",
                w4_media_int_2 = "w4_q49_2",
                w4_media_int_3 = "w4_q49_5",
                w4_media_int_4 = "w4_q49_6"
                )
lookup <- c(pol_cyn, eu_att1, eu_att2, econ_eval, media_tv, media_paper, media_int)

rename(EU_2014_cleaned, all_of(lookup))
EU_2014_cleaned

```

## Make the dataset longer by introducing the "wave" column

```{r}
EU_2014_cleaned <- EU_2014_cleaned |>
  pivot_longer(
    cols = w1_most_important_issue:last_col(),   # Selects from this column to the very last one
    
    
    names_to = c("wave", ".value"),
    names_pattern = "w(.)_(.*)"
  )
EU_2014_cleaned
```

## Testing values and splitting the original file

```{r}

#testing all variables for distinct values to identify variables that can be moved to the second file EXCLUDING variables that are part of waves
distinct()

# take all stable variables based on results of previous line 
demographics <- EU_2014_renamed |>
  select(
    intnr, respnr, sample, waves,
    starts_with("weight_"),  # Include all 4 weight columns
    gender, age, education, region, family_size, pol2012
  )

# Now we take the rest of the variables
survey_data <- EU_2014_renamed |>
  select(!c(sample, waves,gender, age, education, region, family_size, pol2012, starts_with("weight_") )
  )
```

## Primary key table for both?

TBA

QUESTIONS:

Do we need to do joints? How would we approach it?

To what extent should it be undersdtandable without the original documentation? As in do we need to include scales for variables in description
