---
title: "Group project merged"
format: html
editor: visual
---

## Group: EU (A)

## 

```{r}
# Importing tideverse
library(tidyverse)
```

## Importing the dataset

```{r}
# Load data set
EU_2014_cleaned <- read_csv('EU2014/All waves GENERAL.csv')
```

## RQs overview 

1.  To what extent is people's attitude toward the EU, people's economic evaluation toward the EU, and their political cynicism developed throughout the EU election?

2.  To what extent is people's attitude toward the EU, people's economic evaluation toward the EU and their political cynicism related to their media use pattern?

3.  How does the intention to vote differ between EU and local elections, and what is the relationship between the difference and national identity, attitude towards globalisation and anti-immigrant attitudes 6 months prior to the EU elections?

4. How does the readership of Dutch media outlets differ in their attitudes regarding migration?

5. How do Dutch media outlets cover migration?

    \

## Variables needed - ASK TOMORROW IF WE SHOULD KEEP ONLY WHAT WE ARE USING

## Renaming demographics

```{r}
# giving columns informative names, translating dutch names and lowercasing all letters: DEMOGRAPHICS AND DATA SET INFO
EU_2014_cleaned <- EU_2014_cleaned |>
rename(
  weight_w1 = GEWICHTA1_w1,
  weight_w2 = GEWICHTA1_w2,
  weight_w3 = GEWICHTA1_w3,
  weight_w4 = GEWICHTA1_w4,
  gender = GSL,
  age = LFT,
  education = OPLA,
  region = NIELSENCBS, 
  family_size = GEZINSGROOTTE,
  w1_date = w1_DATUM,
  w1_time = w1_TIJD,
  w2_date = w2_DATUM,
  w2_time = w2_TIJD,
  w3_date = w3_DATUM,
  w3_time = w3_TIJD,
  w4_date = w4_DATUM,
  w4_time = w4_TIJD,
) 

colnames(EU_2014_cleaned) <- tolower(colnames(EU_2014_cleaned)) # this function changes all column names to lowercase 
                                                                # (more consistent and easy to use)
```

## Parsing values in cells - LETS ASK TOMORROW (based on that Bára's part either stays or needs to be rewritten)

```{r}
# Value will be parsed in only numerical forms
EU_2014_cleaned <- EU_2014_cleaned |> 
  mutate(
    across(c(                                      # we use across() throughout the code to apply functions to multiple columns
              w1_q32_1, w1_q32_1
            ), parse_number)
          )

# We start with parsing variable: Political cynicism
EU_2014_cleaned <- EU_2014_cleaned |> 
  mutate(
    across(c(
              w1_q10_1, w1_q10_2, w1_q10_3, w1_q10_4,
              w2_q7_1, w2_q7_2, w2_q7_3, w2_q7_4,
              w3_q11_1, w3_q11_2, w3_q11_3, w3_q11_4,
              w4_q13_1, w4_q13_2, w4_q13_3, w4_q13_4
            ), parse_number)
          )

# Now parse variable: EU-attitude
EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(across(c(w1_q26_1:w1_q26_9, w1_q27_1:w1_q27_9,
                  w2_q22_1:w2_q22_9, w2_q23_1:w2_q23_9,
                  w3_q28_1:w3_q28_9, w3_q29_1:w3_q29_9,
                  w4_q31_1:w4_q31_9, w4_q32_1:w4_q32_9),
                parse_number)
               )

# For variable: Economic evaluation
EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(across(c(w1_q12, w2_q9, w3_q13, w4_q15),
                parse_number)
               )

# For variable: self reported media exposure (TV)
EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(across(c(w1_q49_1 : w1_q49_10,
                  w2_q44_1 : w2_q44_10,
                  w3_q43_1 : w3_q43_10,
                  w4_q47_1 : w4_q47_10
                  ),
                parse_number)
                )
 # For variable: self reported media exposure (newspaper)
EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(across(c(w1_q50_1 : w1_q50_10,
                  w2_q45_1 : w2_q45_10,
                  w3_q44_1 : w3_q44_10,
                  w4_q48_1 : w4_q48_10
                  ),
                parse_number)
                )
# Finally, for variable: self reported media exposure (Internet)
EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(across(c(w1_q51_1, w1_q51_2, w1_q51_5, w1_q51_6,
                  w2_q46_1, w2_q46_2, w2_q46_5, w2_q46_6,
                  w3_q45_1, w3_q45_2, w3_q45_5, w3_q45_6,
                  w4_q49_1, w4_q49_2, w4_q49_5, w4_q49_6
                  ),
                parse_number)
                )

# parsing barbora's variables
EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(across(c(w1_q54_1, w1_q54_2, w1_q54_3, w1_q56_1, w1_q56_2, w1_q56_3, 
                w1_q42_1:w1_q42_5, w2_q48_1:w2_q48_3, 
                w2_q49_1:w2_q49_3, w2_q39_1:w2_q39_5),
                parse_number)
                )

```

## Adjusting time and date variables

```{r}
# using lubridate to set dates in date format

EU_2014_cleaned <- EU_2014_cleaned |>
  mutate(
    across(c(w1_date, w2_date, w3_date, w4_date), ymd)
  )

```

## Renaming variable names 

```{r}
EU_2014_cleaned <- EU_2014_cleaned |> 
# we need to give all variables informative name so the variables can be pivoted later.
EU_2014_cleaned |> 
  rename(
    w1_nationalidentity_1 = w1_q5_1,
    w1_nationalidentity_2 = w1_q5_2,
    w1_nationalidentity_3 = w1_q5_3,
    w1_nationalidentity_4 = w1_q5_4,
    w1_attitudeglobal_1 = w1_32_1,
    w1_attitudeglobal_2 = w1_32_2,
    w1_attitudeglobal_3 = w1_32_3,
    w1_attitudeglobal_4 = w1_32_4,
    w1_voteintenteu = w1_q34,
    w1_voteintenteu_other = w1_q34_OTHER,
    w1_voteintentlocal = w1_q39,
    w1_voteintentlocal_other = w1_q39_OTHER,
    w1_antiimmigrant_1 = w1_q42_1,
    w1_antiimmigrant_2 = w1_q42_2,
    w1_antiimmigrant_3 = w1_q42_3,
    w1_antiimmigrant_4 = w1_q42_4,
    w1_antiimmigrant_5 = w1_q42_5,
  )

pol_cyn = c(w1_polcyn_1 = "w1_q10_1",
              w1_polcyn_2 = "w1_q10_2",
              w1_polcyn_3 = "w1_q10_3",
              w1_polcyn_4 = "w1_q10_4",
              w2_polcyn_1 = "w2_q7_1",
              w2_polcyn_2 = "w2_q7_2",
              w2_polcyn_3 = "w2_q7_3",
              w2_polcyn_4 = "w2_q7_4",
              w3_polcyn_1 = "w3_q11_1",
              w3_polcyn_2 = "w3_q11_2",
              w3_polcyn_3 = "w3_q11_3",
              w3_polcyn_4 = "w3_q11_4",
              w4_polcyn_1 = "w4_q13_1",
              w4_polcyn_2 = "w4_q13_2",
              w4_polcyn_3 = "w4_q13_3",
              w4_polcyn_4 = "w4_q13_4"
              )
  eu_att1 = c(w1_eu_att1_1 = "w1_q26_1",
              w1_eu_att1_2 = "w1_q26_2",
              w1_eu_att1_3 = "w1_q26_3",
              w1_eu_att1_4 = "w1_q26_4",
              w1_eu_att1_5 = "w1_q26_5",
              w1_eu_att1_6 = "w1_q26_6",
              w1_eu_att1_7 = "w1_q26_7",
              w1_eu_att1_8 = "w1_q26_8",
              w1_eu_att1_9 = "w1_q26_9",
              w2_eu_att1_1 = "w2_q22_1",
              w2_eu_att1_2 = "w2_q22_2",
              w2_eu_att1_3 = "w2_q22_3",
              w2_eu_att1_4 = "w2_q22_4",
              w2_eu_att1_5 = "w2_q22_5",
              w2_eu_att1_6 = "w2_q22_6",
              w2_eu_att1_7 = "w2_q22_7",
              w2_eu_att1_8 = "w2_q22_8",
              w2_eu_att1_9 = "w2_q22_9",
              w3_eu_att1_1 = "w3_q28_1",
              w3_eu_att1_2 = "w3_q28_2",
              w3_eu_att1_3 = "w3_q28_3",
              w3_eu_att1_4 = "w3_q28_4",
              w3_eu_att1_5 = "w3_q28_5",
              w3_eu_att1_6 = "w3_q28_6",
              w3_eu_att1_7 = "w3_q28_7",
              w3_eu_att1_8 = "w3_q28_8",
              w3_eu_att1_9 = "w3_q28_9",
              w4_eu_att1_1 = "w4_q31_1",
              w4_eu_att1_2 = "w4_q31_2",
              w4_eu_att1_3 = "w4_q31_3",
              w4_eu_att1_4 = "w4_q31_4",
              w4_eu_att1_5 = "w4_q31_5",
              w4_eu_att1_6 = "w4_q31_6",
              w4_eu_att1_7 = "w4_q31_7",
              w4_eu_att1_8 = "w4_q31_8",
              w4_eu_att1_9 = "w4_q31_9"
              )
  eu_att2 = c(w1_eu_att2_1 = "w1_q27_1",
              w1_eu_att2_2 = "w1_q27_2",
              w1_eu_att2_3 = "w1_q27_3",
              w1_eu_att2_4 = "w1_q27_4",
              w1_eu_att2_5 = "w1_q27_5",
              w1_eu_att2_6 = "w1_q27_6",
              w1_eu_att2_7 = "w1_q27_7",
              w1_eu_att2_8 = "w1_q27_8",
              w1_eu_att2_9 = "w1_q27_9",
              w1_eu_att2_1 = "w1_q27_1",
              w1_eu_att2_2 = "w1_q27_2",
              w1_eu_att2_3 = "w1_q27_3",
              w1_eu_att2_4 = "w1_q27_4",
              w1_eu_att2_5 = "w1_q27_5",
              w1_eu_att2_6 = "w1_q27_6",
              w1_eu_att2_7 = "w1_q27_7",
              w1_eu_att2_8 = "w1_q27_8",
              w1_eu_att2_9 = "w1_q27_9",
              w3_eu_att2_1 = "w3_q29_1",
              w3_eu_att2_2 = "w3_q29_2",
              w3_eu_att2_3 = "w3_q29_3",
              w3_eu_att2_4 = "w3_q29_4",
              w3_eu_att2_5 = "w3_q29_5",
              w3_eu_att2_6 = "w3_q29_6",
              w3_eu_att2_7 = "w3_q29_7",
              w3_eu_att2_8 = "w3_q29_8",
              w3_eu_att2_9 = "w3_q29_9",
              w4_eu_att2_1 = "w4_q32_1",
              w4_eu_att2_2 = "w4_q32_2",
              w4_eu_att2_3 = "w4_q32_3",
              w4_eu_att2_4 = "w4_q32_4",
              w4_eu_att2_5 = "w4_q32_5",
              w4_eu_att2_6 = "w4_q32_6",
              w4_eu_att2_7 = "w4_q32_7",
              w4_eu_att2_8 = "w4_q32_8",
              w4_eu_att2_9 = "w4_q32_9"
             )
  econ_eval = c(w1_econ_eval = "w1_q12",
                w2_econ_eval = "w2_q9",
                w3_econ_eval = "w3_q13",
                w4_econ_eval = "w4_q15"
              )
  media_tv = c( w1_media_tv_1  = "w1_q49_1",
                w1_media_tv_2  = "w1_q49_2",
                w1_media_tv_3  = "w1_q49_3",
                w1_media_tv_4  = "w1_q49_4",
                w1_media_tv_5  = "w1_q49_5",
                w1_media_tv_6  = "w1_q49_6",
                w1_media_tv_7  = "w1_q49_7",
                w1_media_tv_8  = "w1_q49_8",
                w1_media_tv_9  = "w1_q49_9",
                w1_media_tv_10 = "w1_q49_10",
                w2_media_tv_1  = "w2_q44_1",
                w2_media_tv_2  = "w2_q44_2",
                w2_media_tv_3  = "w2_q44_3",
                w2_media_tv_4  = "w2_q44_4",
                w2_media_tv_5  = "w2_q44_5",
                w2_media_tv_6  = "w2_q44_6",
                w2_media_tv_7  = "w2_q44_7",
                w2_media_tv_8  = "w2_q44_8",
                w2_media_tv_9  = "w2_q44_9",
                w2_media_tv_10 = "w2_q44_10",
                w3_media_tv_1  = "w3_q43_1",
                w3_media_tv_2  = "w3_q43_2",
                w3_media_tv_3  = "w3_q43_3",
                w3_media_tv_4  = "w3_q43_4",
                w3_media_tv_5  = "w3_q43_5",
                w3_media_tv_6  = "w3_q43_6",
                w3_media_tv_7  = "w3_q43_7",
                w3_media_tv_8  = "w3_q43_8",
                w3_media_tv_9  = "w3_q43_9",
                w3_media_tv_10 = "w3_q43_10",
                w4_media_tv_1  = "w4_q47_1",
                w4_media_tv_2  = "w4_q47_2",
                w4_media_tv_3  = "w4_q47_3",
                w4_media_tv_4  = "w4_q47_4",
                w4_media_tv_5  = "w4_q47_5",
                w4_media_tv_6  = "w4_q47_6",
                w4_media_tv_7  = "w4_q47_7",
                w4_media_tv_8  = "w4_q47_8",
                w4_media_tv_9  = "w4_q47_9",
                w4_media_tv_10 = "w4_q47_10"
              )
  media_paper = c(w1_media_np_1  = "w1_q50_1",
                  w1_media_np_2  = "w1_q50_2",
                  w1_media_np_3  = "w1_q50_3",
                  w1_media_np_4  = "w1_q50_4",
                  w1_media_np_5  = "w1_q50_5",
                  w1_media_np_6  = "w1_q50_6",
                  w1_media_np_7  = "w1_q50_7",
                  w1_media_np_8  = "w1_q50_8",
                  w1_media_np_9  = "w1_q50_9",
                  w1_media_np_10 = "w1_q50_10",
                  w2_media_np_1  = "w2_q45_1",
                  w2_media_np_2  = "w2_q45_2",
                  w2_media_np_3  = "w2_q45_3",
                  w2_media_np_4  = "w2_q45_4",
                  w2_media_np_5  = "w2_q45_5",
                  w2_media_np_6  = "w2_q45_6",
                  w2_media_np_7  = "w2_q45_7",
                  w2_media_np_8  = "w2_q45_8",
                  w2_media_np_9  = "w2_q45_9",
                  w2_media_np_10 = "w2_q45_10",
                  w3_media_np_1  = "w3_q44_1",
                  w3_media_np_2  = "w3_q44_2",
                  w3_media_np_3  = "w3_q44_3",
                  w3_media_np_4  = "w3_q44_4",
                  w3_media_np_5  = "w3_q44_5",
                  w3_media_np_6  = "w3_q44_6",
                  w3_media_np_7  = "w3_q44_7",
                  w3_media_np_8  = "w3_q44_8",
                  w3_media_np_9  = "w3_q44_9",
                  w3_media_np_10 = "w3_q44_10",
                  w4_media_np_1  = "w4_q48_1",
                  w4_media_np_2  = "w4_q48_2",
                  w4_media_np_3  = "w4_q48_3",
                  w4_media_np_4  = "w4_q48_4",
                  w4_media_np_5  = "w4_q48_5",
                  w4_media_np_6  = "w4_q48_6",
                  w4_media_np_7  = "w4_q48_7",
                  w4_media_np_8  = "w4_q48_8",
                  w4_media_np_9  = "w4_q48_9",
                  w4_media_np_10 = "w4_q48_10"
                 )
  media_int = c(w1_media_int_1 = "w1_q51_1",
                w1_media_int_2 = "w1_q51_2",
                w1_media_int_3 = "w1_q51_5",
                w1_media_int_4 = "w1_q51_6",
                w2_media_int_1 = "w2_q46_1",
                w2_media_int_2 = "w2_q46_2",
                w2_media_int_3 = "w2_q46_5",
                w2_media_int_4 = "w2_q46_6",
                w3_media_int_1 = "w3_q45_1",
                w3_media_int_2 = "w3_q45_2",
                w3_media_int_3 = "w3_q45_5",
                w3_media_int_4 = "w3_q45_6",
                w4_media_int_1 = "w4_q49_1",
                w4_media_int_2 = "w4_q49_2",
                w4_media_int_3 = "w4_q49_5",
                w4_media_int_4 = "w4_q49_6"
                )
lookup <- c(pol_cyn, eu_att1, eu_att2, econ_eval, media_tv, media_paper, media_int)

rename(EU_2014_cleaned, all_of(lookup))
EU_2014_cleaned

EU_2014_cleaned <- EU_2014_cleaned |>
  rename(
    w1_most_important_issue = w1_q1,
    w2_most_important_issue = w2_q1,
    w3_most_important_issue = w3_q1,
    w4_most_important_issue = w4_q1)

# using rename_with to rename multiple columns, gsub specifies which pattern should be replaced with what
EU_2014_cleaned <- EU_2014_cleaned |>
    rename_with(function(x) gsub("w1_q54", "w1_comfort_muslims", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w1_q56", "w1_comfort_poles", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q48", "w2_comfort_muslims", x, fixed = TRUE)) |>
    rename_with(function(x) gsub("w2_q49", "w2_comfort_poles", x, fixed = TRUE)) |>
    rename(
      w1_ethnic_minority = w1_q68) |>
    rename(
      w1_ethnic_minority_specification = w1_q68_yes) |>
    rename_with(function(x) gsub("q39", "anti_immigrant_attitudes", x, fixed = TRUE)) |>
    rename(
      w1_immigrant_followup = w1_q43) |>
    rename(
      w2_immigrant_followup = w2_q40) |>
    rename(
      w2_media_trust_rtl = w2_q27_1,
      w2_media_trust_nos = w2_q27_2,
      w2_media_trust_telegraaf = w2_q28_1,
      w2_media_trust_nrc = w2_q28_2,
      w2_media_trust_volkskrant = w2_q28_6,
      w2_media_trust_nunl = w2_q28_11
    )

```

## Make the dataset longer by introducing the "wave" column

```{r}
EU_2014_cleaned <- EU_2014_cleaned |>
  pivot_longer(
    cols = c(starts_with("w1_"), starts_with("w2_"), starts_with("w4_"), starts_with("w5_"))
    names_to = c("wave", ".value"),
    names_pattern = "w(.)_(.*)"
  )
EU_2014_cleaned
```

## Testing values and splitting the original file

```{r}

#testing all variables for distinct values to identify variables that can be moved to the second file EXCLUDING variables that are part of waves
distinct()

# take all stable variables based on results of previous line 
demographics <- EU_2014_renamed |>
  select(
    intnr, respnr, sample, waves,
    starts_with("weight_"),  # Include all 4 weight columns
    gender, age, education, region, family_size, pol2012
  )

# Now we take the rest of the variables
survey_data <- EU_2014_renamed |>
  select(!c(sample, waves,gender, age, education, region, family_size, pol2012, starts_with("weight_") )
  )
```

## Primary key table for both?

TBA

QUESTIONS:

Do we need to do joints? How would we approach it?

To what extent should it be undersdtandable without the original documentation? As in do we need to include scales for variables in description


# Content analysis 

## Libraries

```{r}
library(tidyverse)
```

## Reading in the data

```{r}
# read in the content analysis data 

ca <- read.csv('EU2014/Dataset MCA EPE 2014 NL FINAL.csv')                    
```

## Cleaning

```{r}
# lowercasing column names

colnames(ca) <- tolower(colnames(ca))
```

```{r}

# selecting variables needed for analysis

ca <- ca |> 
  select(
    v4,
    v3a,
    v3b,
    v3c,
    v6_cleaned,
    nl1a:nl1f,
    nl2_1_1:nl2_4_3,
    nl3,
    nl4_1_1:nl4_4_3,
    nl5
  )

#view(ca)
```

### Cleaning dates and times

```{r}
# replacing year numbers 

ca$v3c <- replace(ca$v3c, ca$v3c == 14, values = 2014)
ca$v3c <- replace(ca$v3c, ca$v3c == 13, values = 2013)

#view(ca)
```

```{r}
# using lubridate to set dates in date format

ca <- ca |> 
  mutate(date = make_datetime(v3c, v3b, v3a),.keep = "unused", .before = v4)

```

### Renaming variables

```{r}

#renaming variables

ca <- ca |>
  rename(
    outlet = v4,
    topic = v6_cleaned,
    fear = nl1a,
    anger = nl1b,
    disgust = nl1c,
    hope = nl1d,
    frustration = nl1e,
    surprise = nl1f,
    mention_muslim_general_netherlands = nl2_1_1,
    mention_muslim_general_elweshere = nl2_1_2,
    mention_muslim_general_home = nl2_1_3,
    mention_muslim_moroccans_netherlands = nl2_2_1,
    mention_muslim_moroccans_elsewhere = nl2_2_2,
    mention_muslim_moroccans_home = nl2_2_3,
    mention_muslim_turkish_netherlands = nl2_3_1,
    mention_muslim_turkish_elsewhere = nl2_3_2,
    mention_muslim_turkish_home = nl2_3_3,
    mention_muslim_other_netherlands = nl2_4_1,
    mention_muslim_other_elsewhere = nl2_4_2,
    mention_muslim_other_home = nl2_4_3,
    mention_east_poles_netherlands = nl4_1_1,
    mention_east_poles_elweshere = nl4_1_2,
    mention_east_poles_home = nl4_1_3,
    mention_east_eu_netherlands = nl4_2_1,
    mention_east_eu_elweshere = nl4_2_2,
    mention_east_eu_home = nl4_2_3,
    mention_east_general_netherlands = nl4_3_1,
    mention_east_general_elweshere = nl4_3_2,
    mention_east_general_home = nl4_3_3,
    mention_east_noneu_netherlands = nl4_4_1,
    mention_east_noneu_elweshere = nl4_4_2,
    mention_east_noneu_home = nl4_4_3,
    evaluation_muslims = nl3,
    evaluation_eastern_europeans = nl5
    ) 

```

### Filtering rows needed

```{r}
# filtering rows needed for the analysis (Dutch media outlets)

ca <- ca |>
  filter(
    (outlet == "NRC Handelsblad") |
    (outlet == "de Volkskrant") |
    (outlet == "de Telegraaf") |
    (outlet == "NOS Journaal") |
    (outlet == "RTL Nieuws") |
    (outlet == "nu.nl")
  )
```

### 

```{r}
# replacing blank cells with NA
ca$evaluation_muslims[ca$evaluation_muslims==" "] <- NA
ca$evaluation_eastern_europeans[ca$evaluation_eastern_europeans==" "] <- NA
```

```{r}
# moving evaluation columns to the front to exclude them from pivoting
ca <- ca |>
  relocate(starts_with("evaluation"), .before = mention_muslim_general_netherlands)
  
```

```{r}
# create a mention column that will indicate whether or not a group is mentioned
# create a type column that will indicate which group is mentioned
ca <- ca |>  
  pivot_longer(
    cols = mention_muslim_general_netherlands:last_col(),   # Selects the mention muslim columns
    names_to = "type",
    values_to = "mention"
  )
  
```

```{r}
# separating the type column to multiple variables
ca <- ca |>  
  separate_wider_delim(
  type,
  delim = "_",
  names = c("trash","group", "subgroup", "location"),
  )
  
```

```{r}
# droppin the trash column
ca <- ca |>  
 select(!trash)
  
```

```{r}
# changing categorical variables into factors
ca |>
 mutate_at(c(outlet:mention), as.factor)
```

```{r}
# checking levels
ca |>
  distinct(outlet)

#renaming levels

```
